Aileens Code

### 2023-04-22 AileensCode.Rmd
a

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r cars}

```{r delete}
# Use Information Gain for variable selection
library(MASS)
fit_lm = lm(value~, data=train)
stepAIC(fit_lm, direction="backward", trace=FALSE)
stepAIC(fit_lm, direction="forward", trace=FALSE)
stepAIC(fit_lm, direction="both", trace=FALSE)

# Use Recursive Feature Elimination method
set.seed(123)
cparam = rfeControl(functions=lmFuncs, method='repeatedcv', repeats=5, number=10, verbose=FALSE, returnResamp='all')
profile=rfe(x=train_scaled, y=as.matrix(train$value), sizes=c(1:20),rfeControl=cparam)

# Use Lasso for variable selection X
y=train[,2]
library(glmnet)
feat_mod_select = cv.glmnet(train_scaled, train$value, standardize=TRUE, alpha=1)
as.matrix(coef(features,features$lambda.min))

# fit randfom forest and get var. importance based on mean decr. in accuracy
set.seed(123)
library(party)
train_num = train[,2:50] |> dplyr::select(where(is.numeric))
cf1 = cforest(value ~ ., data=train_num, control=cforest_unbiased(mtry=2, ntree=50))
# adj for corr. btw predictors
varimp(cf1, conditional=TRUE)
# more robust towards class imbalance
varimpAUC(cf1)
```

```
